### 2018-07-06 README.rmd
issues/pulls links + pkre-build site

Development versions can be installed from GitHub:
```{r eval=FALSE}
devtools::install_github("corybrunson/ggalluvial", build_vignettes = TRUE)
```
The
[optimization branch](https://github.com/corybrunson/ggalluvial/tree/optimization) contains a development version with experimental functions to reduce the number or area of alluvial overlaps (see issue [#6](/../../issues/6)). Install it as follows:
```{r eval=FALSE}
devtools::install_github("corybrunson/ggalluvial", ref = "optimization")
```

@@

Issues and pull requests are more than welcome! Pretty much every fix and feature of this package derives from a problem or question posed by someone with datasets or design goals i hadn't anticipated.

>>>>

Development versions can be installed from GitHub:
```{r eval=FALSE}
devtools::install_github("corybrunson/ggalluvial", build_vignettes = TRUE)
```
The
[optimization branch](https://github.com/corybrunson/ggalluvial/tree/optimization) contains a development version with experimental functions to reduce the number or area of alluvial overlaps (see issue [#6](https://github.com/corybrunson/ggalluvial/issues/6)). Install it as follows:
```{r eval=FALSE}
devtools::install_github("corybrunson/ggalluvial", ref = "optimization")
```

@@

[Issues](https://github.com/corybrunson/ggalluvial/issues) and [pull requests](https://github.com/corybrunson/ggalluvial/pulls) are more than welcome! Pretty much every fix and feature of this package derives from a problem or question posed by someone with datasets or design goals i hadn't anticipated.
